---
title: "Comparing heights of male and female students"
author: "Imelds"
date: "2022-09-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "..")
library(tidyverse) # load our packages here
```

## Introduction

Investigation of the distribution of heights of male and female TCD post-graduate students.
Analysing to see if male and female heights differ significantly.

## Data

Data was a small sample (only 33 observations).

Data is collected face-to-face, but self-reported and not verified.  Height was recorded to nearest cm.  Sex was recorded as 0  = male, 1 = female.  No other options were given.


Import here the data and describe it. Include in the chunk below a brief summary

```{r data, echo = FALSE} 
# echo = FALSE doesn't show code, does show output
# copy paste the code to import the data


data <- read.csv("Data/height.csv")
knitr::kable(head(data)) #try to copy and paste here a relevant line of code as 
# an argument to the kable() function.
```

## Analysis

Describe how we analysed the data. You might wish to add a snippet of code within your analysis, such as `r round(mean(data$height), 2)`. 

Include below a relevant visualisation for the mean. 

```{r data visualisation, echo = FALSE}
data$sex_f <- as.factor(data$sex) # Convert to factor - add a new column to data frame
levels(data$sex_f) <- c("M", "F") # Change the levels

data %>% # Tidyverse method for grouping
  group_by(sex_f) %>%
  summarise(mean = mean(height))

# Visualise

# can see eg that no crossover in interquartile ranges
boxplot(data$height ~ data$sex_f, # here we use formula notation to group
        main = "Boxplot of Height by Sex",
        ylab = "cm",
        xlab = "")



```

Let's also include some analysis of whether men and women are, on average, of different heights. We might add the output of the t test in a chunk

```{r t test}

```

And also a visualisation - the box plot would be good here.

```{r box plot, echo = FALSE}

```

## Conclusion

Add a few words in conclusion. What weaknesses might there be in your research? What further questions might you answer?